Towards the near-infrared detection of brown dwarf companions\thanks{Based on observations collected at the European Organisation for Astronomical Research in the Southern Hemisphere under ESO programme 089.C-0977(A)}

### 2018-07-23 drafts/aanda_nir-companions.tex
add old paper format

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Basic setup. Most papers should leave these options alone.
\documentclass[fleqn,usenatbib]{mnras}

% MNRAS is set in Times font. If you don't have this installed (most LaTeX
% installations will be fine) or prefer the old Computer Modern fonts, comment
% out the following line
\usepackage{newtxtext,newtxmath}
% Depending on your LaTeX fonts installation, you might get better results with one of these:
%\usepackage{mathptmx}
%\usepackage{txfonts}

% Use vector fonts, so it zooms properly in on-screen viewing software
% Don't change these lines unless you know what you are doing
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}

%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%

% Only include extra packages if you really need them. Common packages are:
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
%\usepackage{amssymb}	% Extra maths symbols
\usepackage[para]{threeparttable}
\usepackage{hyperref}
\usepackage{natbib}
\usepackage{booktabs}
\usepackage{color}
\usepackage{fix-cm}
%\usepackage{caption}   % Caption is required to aviod errors.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%

% Please keep new commands to a minimum, and use \newcommand not \def to avoid
% overwriting existing commands. Example:
%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared
\newcommand*\bl{\color{blue}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
%\title[Short title, max. 45 characters]{MNRAS \LaTeXe\ template -- title goes here}
\title[Towards the nIR detection of BD companions]{Towards the near-infrared detection of brown dwarf companions: Exploring methods to detect low mass stellar companions from blended spectra \thanks{Based on observations collected at the European Organisation for Astronomical Research in the Southern Hemisphere under ESO programme 089.C-0977(A)}}
%\subtitle{Exploring methods to detect low mass stellar companions from blended spectra}
% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor

\author[J. J. Neal et al.]{
J. J. Neal$^{1,2}$\thanks{E-mail: jason.neal@astro.up.pt}
P. Figueira$^{3,1}$ 
N. C. Santos$^{1,2}$
C. Melo$^{3}$
\\
% List of institutions
$^{1}$Instituto de Astrof\'{\i}sica e Ci\^encias do Espa\c{c}o, CAUP, Universidade do Porto, Rua das Estrelas, PT4150-762 Porto, Portuga\\l
$^{2}$Departamento de F\'{\i}sica e Astronomia, Faculdade de Ci\^{e}ncias, Universidade do Porto, Portugal\\
$^{3}$European Southern Observatory, Alonso de C\'{o}rdova 3107, Vitacura, Casilla 19001, Santiago 19, Chile\\
}

% These dates will be filled out by the publisher
\date{Accepted XXX. Received YYY; in original form ZZZ}

% Enter the current year, for the copyright statements etc.
\pubyear{2018}

% Don't change these lines
\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle

% Abstract of the paper
\begin{abstract}
    {\bl A}We perform an exploratory study on how to directly detect the near-infrared spectrum of candidate brown dwarf (BD) companions around FGK stars to measure or constrain their masses, thereby asserting their stellar nature or discarding it. {\bl B}We explore two different methods to probe the faint spectra of BD companions. The first technique involves the direct subtraction of two observations shifted to mutually cancel out the spectra of the host star. The second technique applies a \(\chi^{2}\) fit to the individual observations with a synthetic binary model comprised of two PHOENIX-ACES spectra, representing the spectra from the host and companion. The observed spectra are wavelength calibrated and corrected for the atmospheric absorption with the aid of synthetic telluric models.
    {\bl C}The direct subtraction method failed to detect the signature of the companions. The \(\chi^{2}\) technique developed here is able to fit the component for the host star but unable to successfully detect the faint spectra of even the largest companion in our sample. We explore how the companion recovery performs on simulated observations and discuss reasons for the non-detection observed. From the synthetic spectra we determine the upper mass limit for the companions to be around \(\rm 600^{+20}_{-40}~M_{Jup}\) as the limitation of this technique for the data we had on hand. {\bl D}This work highlights the challenges in the spectral detection of faint BD companions. We explore the limitations of the direct subtraction method in the case of small RV separation, and attempt companion recovery at low companion/host flux ratios below 3\%, finding a high upper mass limit from the technique. {\bl This is a simple template for authors to write new MNRAS papers.
The abstract should briefly describe the aims, methods, and main results of the paper.
It should be a single paragraph not more than 250 words (200 words for Letters).
No references should appear in the abstract.}
\end{abstract}

\begin{keywords}
brown dwarfs -- binaries: spectroscopic -- infrared: stars -- techniques: spectroscopic -- methods: miscellaneous
\end{keywords}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%% BODY OF PAPER %%%%%%%%%%%%%%%%%%

@@

A paucity of BD companions exists in short period orbits around Sun-like stars (\(\lesssim5 \)\,AU), compared to stellar or planetary companions, termed the \emph{brown dwarf desert}~\citep{halbwachs_exploring_2000,zucker_analysis_2001,sahlmann_search_2011}. As the number of known BDs orbiting solar type stars is low, the characterization of benchmark BDs in the brown dwarf desert~\citep[e.g.][]{crepp_trends_2016} is beneficial in understanding this sub-stellar population and to help constrain formation and evolution theories~\citep{whitworth_formation_2007}. The BD desert also provides a greater challenge as it reduces the amount of good BD candidates to study.

BDs in binary systems, unlike free-floating BDs, allow for the determination of their masses, when complemented with radial velocity (RV) and astrometry measurements. The RV technique provides the mass lower-limit (\(\textrm{M}_{2}\sin{i} \)) of binary and planetary companions, while complementary astrometry measurements can often provide mass upper-limits~\citep[e.g.][]{sahlmann_search_2011}. Measuring or tightening the constraints of BD masses improves the understanding of mass dependence on BD formation processes. For instance, there is growing evidence that the larger giant planets and BD companions do not follow the well known metallicity-giant planet correlation seen in main-sequence stars with planets~\citep[e.g.][]{santos_spectroscopic_2004,santos_observational_2017, maldonado_searching_2017}. Photometry along with stellar evolution models~\citep[e.g.][]{baraffe_evolutionary_2003,allard_btsettl_2013} can also be used to estimate the mass of BD companions~\citep[e.g.][]{moutou_eccentricity_2017} if there is sufficient orbital separation, and a precise determination of the age~\citep{soderblom_ages_2010}.

Recently, there has been a renewed interest in BD candidates triggered by exoplanetary searches. While several works found similar properties on the two populations, like a similar density~\citep{hatzes_definition_2015}, others found intriguing differences. One of the most recent is the different host metallicity of the Brown Dwarf and giant planet populations~\citep{santos_observational_2017, schlaufman_evidence_2018}, a very strong hint of different formation mechanisms.

@@

Observing in the near-infrared is specifically desirable for the cooler sub-stellar and giant planet companions as their thermal emission is stronger in the infrared compared to the optical. This improves the contrast ratio between the host star and companion, providing favorable conditions for their detection and spectral separation. CRIRES, a high resolution near-infrared spectrograph, has made many prominent advances in recent years with the detection of atmospheric constituents, such as \(\textrm{CO} \) and \(\textrm{H}_{2}\textrm{O} \), atmospheric winds and thermal profiles, rotation and orbital motion, for both transiting and non-transiting planets~\citep[e.g.][]{snellen_orbital_2010, brogi_signature_2012, rodler_weighing_2012, dekok_detection_2013, brogi_carbon_2014, snellen_fast_2014, piskorz_evidence_2016, brogi_rotation_2016}.

The higher temperature and relatively larger size of BDs compared to giant-planets makes the development of spectral recovery techniques for BD companions a logical step towards the spectroscopic detection of planetary atmospheres. There has been the recent installation and continued development of many new high-resolution near-InfraRed (nIR) spectrographs, such as, CARMENES~\citep{quirrenbach_carmenes_2014}, NIRPS~\citep{bouchy_nearinfrared_2017} or SPIRou~\citep{artigau_spirou_2014}, as well as, the CRIRES+~\citep{dorn_crires_2016} upgrade. These new instruments motivate the study of nIR-oriented methodologies for spectral recovery, and are of high importance due to the larger planet-to star flux ratio in the near-IR than in the visible.

@@

\section{Motivation and target selection}
\label{sec:motivation}
The work of~\citet{sahlmann_search_2011} identified several candidate brown dwarf companions of FGK stars with \(\rm M_2 \sin{i}\) values >\(\rm 10~M_{Jup}\). Seven candidates were selected for observation in order to identify their stellar nature. The target host stars are presented in Table~\ref{tab:starparams} with their stellar parameters, while the companion orbital parameters are provided in Table~\ref{tab:orbitparams}.

We note that some of these orbital parameters have been refined in the literature since observations took place. For example three candidates have had their masses refined in recent works. The companion to {HD 211847} was determined to be a low mass star with an \(\rm M_2=155~M_{Jup}\)~\citep{moutou_eccentricity_2017}, while the companion to {HD 4747} was found to have a mass of \(\rm M_2=60~M_{Jup}\)~\citep{crepp_trends_2016}. The two companions of {HD 202206} (B and c) were found to have masses of \(\rm M_B =93.6~M_{Jup}\) and \(\rm M_c = 17.9~M_{Jup}\), respectively, classifying {HD 202206}c as a ``circumbinary brown dwarf''~\citep{benedict_hd_2017}. These targets with recently refined masses create good benchmarks for us to compare any results of the techniques developed in this paper, and show that these masses do span the BD -- low mass star range. All target companions except {HD 162020} (P=8.4 days) are in (very) long period orbits (P=0.7--38 years) with masses (or \(M\sin{i}\)) greater than \(\rm 10~M_{Jup}\).

\textit{K}-band spectra were obtained with the goal to achieve a direct detection of the companion spectra through the application of a spectral-differential approach. Doing so would enable a further constraint to be placed on their masses. The \textit{K}-band is used to achieve a high contrast relative to the host star, detected in the extreme V-K color indexes (>7.8).

% Table of stellar parameters
\input{tables/stellarparameters}

% Table of orbit parameters
\input{tables/orbitalparameters}

% Table of estimates of parameters
\input{tables/estimatedparameters}

@@

\subsection{CRIRES data}
\label{subsec:CRIRES} 
Observations were performed with the CRIRES instrument~\citep{kaeufl_crires_2004} configured to observe a narrow wavelength domain of the \textit{K}-band between 2120--2160~nm using the {Ks} and the {Hx5e-2} filters. The slit width of \(0.4\sec \) resulted in an instrumental resolving power of \(\rm R=50\,000\), with no adaptive optics to ensure that the slit was entirely covered by each target. This prevents strong slit illumination variations that could change the shape of spectral lines.

@@

@@

One possible explanation for the artifacts present is an instrumental effect, such as instrument glow. This is known to affect CRIRES and included in the data reduction cookbook~\citep{smoker_very_2012}. These artifacts in the \textit{K}-band spectra were not observed in previous works in the \textit{H}-band using this pipeline and as such may have a wavelength dependent affect, as the higher wavelength nIR is more susceptible to thermal instrument glow.

\subsubsection{Wavelength calibration}
\label{subsec:wave_cal}
There is a known issue with the wavelength calibration from the CRIRES Th-Ar calibrations~\citep{kerber_laboratory_2009}, due to the low density of Th-AR lines in the near-infrared and the alignment with the detectors narrow wavelength range (e.g.\ CRIRES-POP~\citep{nicholls_crirespop_2017}).
Therefore, we use the telluric absorption lines present in each observation as the wavelength reference. Instead of directly using the HITRAN database~\citep{rothman_hitran2012_2013} for the line positions of the telluric spectra (e.g.~\citep{brogi_signature_2012,brogi_carbon_2014,dekok_detection_2013}), we use TAPAS atmospheric transmission models~\citep{bertaux_tapas_2014} obtained for each observation. These in turn use the HITRAN database but include atmospheric profiles and physical measurements to model the telluric absorption strength.

@@

The wavelength solution was obtained by fitting a second order polynomial, shown to be sufficient for higher precision RV studies~\citep[e.g.][]{bean_groundbased_2010, figueira_radial_2010}, to the centroid values \(\{\mu(x), \mu(\lambda)\} \) obtained from the telluric component of the observed spectra and telluric model respectively.

@@

We note that there are many variations on this wavelength-calibration technique including those integrated within programs such as TelFit~\citet{gullikson_correcting_2014}, and ESOs Molecfit~\citet{smette_molecfit_2015}, that perform telluric correction and re-calibrate the wavelength axis themselves.

@@

Secondly, we mask out any remaining artifacts present in the spectra and the centers of deep telluric lines where telluric correction was not corrected properly, sometimes resulting in ``emission-like'' peaks in the corrected spectrum. These factors combined result in masking out around a further 10\% of the observed spectra.

@@

We are aware that using these radii radii has its limitations, since as stated previously, there is a degeneracy in BD mass, age, and luminosity of the companion, and in particular a combination of radius-mass and radius-age relationships~\citep{sorahana_radii_2013}. Using the PHOENIX-ACES model effective radius does not allow for any independent age constraints to be incorporated, or allow for any variability in the radii to account for uncertainties.

>>>>

%!TEX root = nir-companions.tex
% aa.dem
% AA vers. 9.0, LaTeX class for Astronomy & Astrophysics
%                                                       (c) EDP Sciences
%-----------------------------------------------------------------------

%\documentclass[referee]{aa} % for a referee version
\documentclass{aa}

\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage[varg]{txfonts}
\usepackage{hyperref}
\usepackage{natbib}
\usepackage{booktabs}
%\usepackage{multirow}
\usepackage{color}
\newcommand*\bl{\color{blue}}

% to follow the A&A style
\bibpunct{(}{)}{;}{a}{}{,}  % chkteX 9

\begin{document}

   \title{Towards the near-infrared detection of brown dwarf companions\thanks{Based on observations collected at the European Organisation for Astronomical Research in the Southern Hemisphere 
           under ESO programme 089.C-0977(A)}}
   \subtitle{Exploring methods to detect low mass stellar companions from blended spectra}

   \titlerunning{Towards the nIR detection of BD companions}
   \authorrunning{J.J. Neal et. al.}

   \author{J. J. Neal\inst{\ref{IA}, \ref{FCUP}}\thanks{\email{jason.neal@astro.up.pt}}
          \and P. Figueira\inst{\ref{ESO/Chile}, \ref{IA}} 
          \and N. C. Santos\inst{\ref{IA}, \ref{FCUP}}
          \and C. Melo\inst{\ref{ESO/Chile}}
          }

   \institute{Instituto de Astrof\'{\i}sica e Ci\^encias do Espa\c{c}o, CAUP, Universidade do Porto, Rua das Estrelas, PT4150-762 Porto, Portugal\label{IA}
            \and Departamento de F\'{\i}sica e Astronomia, Faculdade de Ci\^{e}ncias, Universidade do Porto, Portugal\label{FCUP}
            \and European Southern Observatory, Alonso de C\'{o}rdova 3107, Vitacura, Casilla 19001, Santiago 19, Chile\label{ESO/Chile}
            }

   \date{Received ... /
            Accepted ...}

% \abstract{}{}{}{}{}
% 5 {} token are mandatory

\abstract%
% context heading (optional)
% {} leave it empty if necessary
{}
% aims heading (mandatory)
 {We perform an exploratory study on how to directly detect the near-inf\right ared spectrum of candidate brown dwarf (BD) companions around FGK stars to measure or constrain their masses, thereby asserting their stellar nature or discarding it.}
% methods heading (mandatory)
 {We explore two different methods to probe the faint spectra of BD companions. The first technique involves the direct subtraction of two observations shifted to mutually cancel out the spectra of the host star. The second technique applies a \(\chi^{2}\) fit to the individual observations with a synthetic binary model comprised of two PHOENIX-ACES spectra, representing the spectra from the host and companion. The observed spectra are wavelength calibrated and corrected for the atmospheric absorption with the aid of synthetic telluric models.}
% results heading (mandatory)
 {The direct subtraction method failed to detect the signature of the companions. The \(\chi^{2}\) technique developed here is able to fit the component for the host star but unable to successfully detect the faint spectra of even the largest companion in our sample. We explore how the companion recovery performs on simulated observations and discuss reasons for the non-detection observed. From the synthetic spectra we determine the upper mass limit for the companions to be around \(\rm 600^{+20}_{-40}~M_{Jup}\) as the limitation of this technique for the data we had on hand.}
% conclusions heading (optional), leave it empty if necessary
 {This work highlights the challenges in the spectral detection of faint BD companions. We explore the limitations of the direct subtraction method in the case of small RV separation, and attempt companion recovery at low companion/host flux ratios below 3\%, finding a high upper mass limit from the technique.}

  \keywords{(stars:) binaries: spectroscopic -- (stars:) brown dwarfs -- Infrared: stars  -- techniques: spectroscopic -- methods: miscellaneous}

  \maketitle
%
%-------------------------------------------------------------------

@@

A paucity of BD companions exists in short period orbits around Sun-like stars (\(\lesssim5 \)\,AU), compared to stellar or planetary companions, termed the \emph{brown dwarf desert}~\citep{halbwachs_exploring_2000,zucker_analysis_2001,sahlmann_search_2011}. As the number of known BDs orbiting solar type stars is low, the characterization of benchmark BDs in the brown dwarf desert \citep[e.g.][]{crepp_trends_2016} is beneficial in understanding this sub-stellar population and to help constrain formation and evolution theories~\citep{whitworth_formation_2007}. The BD desert also provides a greater challenge as it reduces the amount of good BD candidates to study.

BDs in binary systems, unlike free-floating BDs, allow for the determination of their masses, when complemented with radial velocity (RV) and astrometry measurements.  The RV technique provides the mass lower-limit (\(\textrm{M}_{2}\sin{i} \)) of binary and planetary companions, while complementary astrometry measurements can often provide mass upper-limits\ \citep[e.g.][]{sahlmann_search_2011}. Measuring or tightening the constraints of BD masses improves the understanding of mass dependence on BD formation processes. For instance, there is growing evidence that the larger giant planets and BD companions do not follow the well known metallicity-giant planet correlation seen in main-sequence stars with planets~\citep[e.g.][]{santos_spectroscopic_2004,santos_observational_2017, maldonado_searching_2017}. Photometry along with stellar evolution models~\citep[e.g.][]{baraffe_evolutionary_2003,allard_btsettl_2013} can also be used to estimate the mass of BD companions~\citep[e.g.][]{moutou_eccentricity_2017} if there is sufficient orbital separation, and a precise determination of the age~\citep{soderblom_ages_2010}.

Recently, there has been a renewed interest in BD candidates triggered by exoplanetary searches. While several works found similar properties on the two populations, like a similar density \citep{hatzes_definition_2015}, others found intriguing differences. One of the most recent is the different host metallicity of the Brown Dwarf and giant planet populations \citep{santos_observational_2017, schlaufman_evidence_2018}, a very strong hint of different formation mechanisms.

@@

Observing in the near-infrared is specifically desirable for the cooler sub-stellar and giant planet companions as their thermal emission is stronger in the infrared compared to the optical. This improves the contrast ratio between the host star and companion, providing favorable conditions for their detection and spectral separation. CRIRES, a high resolution near-infrared spectrograph, has made many prominent advances in recent years with the detection of atmospheric constituents, such as \(\textrm{CO} \) and \(\textrm{H}_{2}\textrm{O} \), atmospheric winds and thermal profiles, rotation and orbital motion, for both transiting and non-transiting planets \citep[e.g.][]{snellen_orbital_2010, brogi_signature_2012, rodler_weighing_2012, dekok_detection_2013, brogi_carbon_2014, snellen_fast_2014, piskorz_evidence_2016, brogi_rotation_2016}.

The higher temperature and relatively larger size of BDs compared to giant-planets makes the development of spectral recovery techniques for BD companions a logical step towards the spectroscopic detection of planetary atmospheres. There has been the recent installation and continued development of many new high-resolution near-InfraRed (nIR) spectrographs, such as, CARMENES \citep{quirrenbach_carmenes_2014},  NIRPS \citep{bouchy_nearinfrared_2017} or SPIRou \citep{artigau_spirou_2014}, as well as, the CRIRES+ \citep{dorn_crires_2016} upgrade. These new instruments motivate the study of nIR-oriented methodologies for spectral recovery, and are of high importance due to the larger planet-to star flux ratio in the near-IR than in the visible.

@@

\section{Motivation and target selection}
\label{sec:motivation}
The work of \citet{sahlmann_search_2011} identified several candidate brown dwarf companions of FGK stars with \(\rm M_2 \sin{i}\) values >\(\rm 10~M_{Jup}\).  Seven candidates were selected for observation in order to identify their stellar nature. The target host stars are presented in Table~\ref{tab:starparams} with their stellar parameters, while the companion orbital parameters are provided in Table~\ref{tab:orbitparams}.

We note that some of these orbital parameters have been refined in the literature since observations took place. For example three candidates have had their masses refined in recent works. The companion to {HD 211847} was determined to be a low mass star with an \(\rm M_2=155~M_{Jup}\) \citep{moutou_eccentricity_2017}, while the companion to  {HD 4747} was found to have a mass of \(\rm M_2=60~M_{Jup}\) \citep{crepp_trends_2016}. The two companions of {HD 202206} (B and c) were found to have masses of \(\rm M_B =93.6~M_{Jup}\) and \(\rm M_c = 17.9~M_{Jup}\), respectively,  classifying {HD 202206}c as a ``circumbinary brown dwarf'' \citep{benedict_hd_2017}. These targets with recently refined masses create good benchmarks for us to compare any results of the techniques developed in this paper, and show that these masses do span the BD -- low mass star range. All target companions except {HD 162020} (P=8.4 days) are in (very) long period orbits (P=0.7--38 years) with masses (or \(M\sin{i}\)) greater than \(\rm 10~M_{Jup}\).

K-band spectra were obtained with the goal to achieve a direct detection of the companion spectra through the application of a spectral-differential approach. Doing so would enable a further constraint to be placed on their masses. The K-band is used to achieve a high contrast relative to the host star, detected in the extreme V-K color indexes (>7.8).

%% Table of stellar parameters
\begin{table*}
	\centering
	\small
	\caption{Stellar parameters of the target companion's host stars. V is the apparent magnitudes taken from SIMBAD~\citep{wenger_simbad_2000}.}
		\begin{tabular}{l c c r@{$~\pm~$}l r@{$~\pm~$}l r@{$~\pm~$}l r@{$~\pm~$}l c c}
		\toprule
		Star & SpT & V &  \multicolumn{2}{c}{\(T_{\textrm{eff}}\) (K)} &  \multicolumn{2}{c}{logg (cm s\(^{-2} \))}  & \multicolumn{2}{c}{[Fe/H]} &  \multicolumn{2}{c}{\(M_1\) (M\(_{\sun} \))} & Age (Gyr) & Reference\\
		\midrule
        {HD 4747}     & K0V & 7.15 & 5316 & 50 & 4.48 & 0.10  & $-$0.21 & 0.05 & 0.81 & 0.02  & $3.3 \pm 2.3$  & 1, 2, 3  \\ 
		{HD 162020} & K3V & 9.12 & 4723 & 71 & 4.31 & 0.18  & $-$0.10 & 0.03 & 0.74 & 0.07  & $3.1 \pm 2.7$  & 4, 5, 6  \\  
		{HD 167665} & F9V & 6.40 & 6224 & 50 & 4.44 & 0.10  & 0.05       & 0.06 & 1.14 & 0.03  & 0.7 -- 3.6          & 1         \\
		{HD 168443} & G6V & 6.92 & 5617 & 35 & 4.22 & 0.05 & 0.06       & 0.05 & 1.01 & 0.07  & $10.0 \pm 0.3$ & 5, 6     \\ 
		{HD 202206} & G6V & 8.07 & 5757 & 25 & 4.47 & 0.03 & 0.29       & 0.02 & 1.04 & 0.07  & $2.9 \pm 1.0$   & 5, 7     \\ 
		{HD 211847} & G5V & 8.62 & 5715 & 24 & 4.49 & 0.05 & $-$0.08 & 0.02 & 0.92 & 0.07   & 0.1 -- 6.0           & 1, 2, 4 \\ 
		{HD 30501}   & K2V & 7.59  & 5223 & 50 & 4.56 & 0.10 & 0.06       & 0.06 & 0.81 & 0.02  & 0.8 -- 7.0           & 1, 4     \\
		\bottomrule
	\end{tabular} \\
	\tablebib{
	          (1) \citet{sahlmann_search_2011}; (2) \citet{santos_spectroscopic_2005}; (3) \citet{crepp_trends_2016}; (4) \citet{tsantaki_deriving_2013}; (5) \cite{bonfanti_age_2016}; (6) \citet{santos_spectroscopic_2004};
	          (7) \citet{sousa_spectroscopic_2008};
	          }
	\label{tab:starparams}
\end{table*}

	% Table of orbit parameters
	\begin{table*}
		\centering
		\tiny
		\caption{Orbital parameters for the BD companions obtained from the literature.}
		\begin{tabular}{l c r@{$ \,\pm\, $}l r@{$ \,\pm\, $}l r@{$ \,\pm\, $}l r@{$ \,\pm\, $}l r@{$ \,\pm\, $}l cc c c}
		\toprule
		Object  & \(\gamma \)  	& \multicolumn{2}{c}{Period}   & \multicolumn{2}{c}{\(e \) } &  \multicolumn{2}{c}{\(\textrm{K}_{1} \) } &  \multicolumn{2}{c}{\(T_{0} \)}  &  \multicolumn{2}{c}{ \(\omega \) } & \(M_2\sin{i}\) & \(M_2\) & Ref.\\
		 & (km\(^{-1} \)) 	& \multicolumn{2}{c}{(day)}   	&    \multicolumn{2}{c}{}    &  \multicolumn{2}{c}{(ms\(^{-1} \))}   & \multicolumn{2}{c}{ (JD-2\,450\,000) } &  \multicolumn{2}{c}{(deg) } &   \(\rm {M}_{Jup} \)  &   \(\rm {M}_{Jup} \)   & \\
		\midrule
		{HD 4747}       & $0.215 \pm 11 $        	 &  13826.2  &  314.1            &  0.740 & 0.002  	& 755.3   &  12      & 463.1       &  7.3    & 269.1      &  0.6   &  39.6    & 60.2 			  & 1 \\
		{HD 162020}   & $-27.328\pm0.002$  	    &  8.42819  &  $6e^{-5}$   &  0.277 & 0.002   & 1813    &  4        & 1990.68   &  0.01  & 28.4        &  0.2   & 14.4     &     -   			  & 2 \\
		{HD 167665}   & $8.003 \pm 0.008$    	 & 4451.8 & 27.6   				   & 0.340 & 0.005 	  & 609.5   &  3.3     & 6987.6     &  29     & $-$134.3 & 0.9     & 50.3    &     -    			& 3 \\
		{HD 168443}b  & $-0.047\pm0.552$ 		& 58.1124 & $4e^{-4}$  		& 0.529 & 0.001   & 475.13 & 0.9      & 5626.20  &  0.02   & 172.9      & 0.1     & 7.7      &     -    			& 4 \\ 
		{HD 168443}c  & $-0.047\pm0.552$ 		 & 1749.83 & 0.57  			     & 0.211 & 0.002  	 & 297.7  & 0.6      & 5521.3     &  2.2     & 64.9       & 0.5     & 17.1    &     -    			  & 4 \\ 
		{HD 202206}B & 14.721     						& 256.33  &  0.02    		     & 0.432 & 0.001  	  & 567     &  1       & 2176.14    &  0.12   & 161.9     & 0.2  	& 17.4    & $93.2\pm7.3$   & 5, 6\\  
		{HD 202206}c & 14.721    						 & 1260 &  11			        	& 0.22 & 0.03 		  & 41    	& 1          & 3103 		& 452    & 280 		   & 4  	  & 2.3      & $17.9\pm2.9$  & 5, 6\\ 
		{HD 211847} 	 & 6.689\tablefootmark{a} & 7929.4 & 2500  		    	 & 0.685 & 0.068   	  & 291.4   & 12.2   & 12030.1    & 2500   & 159.2 		& 2.0     & 19.2  & 155  				& 3, 7\\
		{HD 30501}  	  & $23.710\pm0.028$         & 2073.6 & 3.0 				& 0.741 & 0.004   	   & 1703.1 & 26.0   & 3851.5 		& 3.0     & 70.4 		& 0.7     & 62.3   & 89.6      			& 3  \\
		\bottomrule
	\end{tabular}
	\tablebib{
	          (1) \citet{crepp_trends_2016}; (2) \citet{udry_coralie_2002}; (3) \citet{sahlmann_search_2011}; 
	          (4) \citet{pilyavsky_search_2011}; (5) \citet{correia_coralie_2005};  (6) \citet{benedict_hd_2017}; (7) \citet{moutou_eccentricity_2017}
	}
	\tablefoot{
	\tablefoottext{a}{fixed}
	}
	\label{tab:orbitparams}
\end{table*}

\begin{table*}
    %\tiny
    \small
    \centering
    \caption{Estimated flux ratios and semi-amplitude of the companion given the companion \(\textrm{M}_{2}/\textrm{M}_{2} \sin{i}\) from Table~\ref{tab:orbitparams}. The flux ratio \(F_{2}/F_{1} \) is calculated using the absolute K-band magnitude difference of the host star to the Baraffe evolutionary model magnitude for the companion mass. The model ages used are those closest to host age value in Table~\ref{tab:starparams}, or the midpoint of the age range. The noise ratio is calculated via \(N_{2}/N_{1} = \sqrt{2} \times\sqrt{F_{1}/F_{2}}\). The orbital properties are calculated using the orbital parameters given above along with the times of observations in Table~\ref{tab:observations}.} 
    \begin{tabular}{l c c c c c c c c}
        \toprule
        &  Estimated  & Estimated &  Estimated & Estimated &  &    \\  % 2017
        Host           & \(\rm F_{2}/F_{1} \)   & \(\rm N_{2}/N_{1} \) (noise ratio) & \(\rm K_2\) &   \(\Delta RV\) & Phase coverage \\
        & K-band     & & (kms\(^{-1}\)) & (ms\(^{-1}\)) & (\%) \\
        \midrule
        {HD 4747}        & \(3\times10^{-4} \)   & 76 &  -10.65 & -  &  -  \\  % 2017
        {HD 162020}   & \(7\times10^{-7} \)   & 1615  &  -98.92\tablefootmark{a} &  2344.24     & 0.28~~  \\  %
        {HD 167665}    & \(2\times10^{-4} \)   &  105    &  -14.47\tablefootmark{a}   &   138.45     & 0.18~~  \\  %  -- \(2\times10^{-5} \)  best case based on age rage.
        {HD 168443b} & \(1\times10^{-16} \)  &    \(1\times10^{8} \)   &  -64.65\tablefootmark{a} &   257.16   & 0.035 \\ 
        {HD 168443c} &  \(1\times10^{-11} \)  &   \(4\times10^{5} \)     &  -18.05\tablefootmark{a}  &   0.95   &  0.001 \\  %(c)
        {HD 202206}B  & \(8\times10^{-7} \)  &   1586 &  -6.79 & 145.17   & 0.74~  \\  %(B)   % May2017
        {HD 202206}c  &  \(5\times10^{-15}\)   &     \(2\times10^{7} \) &   -2.50     &   0.67     &  0.15~  \\  %(B)   % May2017
        {HD 211847}B  &  0.01 &  14   & $-$1.85 & 3.88   & 0.09~  \\  %B % 2017
        {HD 30501}      &  0.002  &  27  &  -16.12    &  1346.46      & 5.8~~  \\
        \bottomrule
    \end{tabular}\\
    \tablefoot{
        \tablefoottext{a}{Maximum \(K_2\) only given \(M_2 \sin{i}\)}
    }
    \label{tab:flux_table}
\end{table*}

@@

\subsection{CRIRES data}
\label{subsec:CRIRES} 
Observations were performed with the CRIRES instrument~\citep{kaeufl_crires_2004} configured to observe a narrow wavelength domain of the K-band between 2120--2160~nm using the Ks and the Hx5e-2 filters. The slit width of \(0.4\sec \) resulted in an instrumental resolving power of \(\rm R=50\,000\), with no adaptive optics to ensure that the slit was entirely covered by each target. This prevents strong slit illumination variations that could change the shape of spectral lines.

@@

\begin{figure}
    \includegraphics[width=\hsize]{images/Bad_pixel_replacement.pdf}  % chktex 8
    \caption{Example of an artifact in the optimally extracted spectra. The top panel contains the 8 normalized nod spectra after optimal extraction, while the middle panel shows the rectangular extraction for the exact same spectra. A vertical offset is included between each spectra. A single large spike in the seventh nod (pink) near pixel 230 creates a wide and noticeable artifact in the optimal extraction. The bottom panel shows the difference between a combined spectrum using the optimal nods only and a combined spectrum in which the seventh nod is replaced with its rectangular counterpart. The nod spectra are in observation order from top to bottom.}
    \label{fig:nod_artifacts}
\end{figure}

@@

One possible explanation for the artifacts present is an instrumental effect, such as instrument glow. This is known to affect CRIRES and included in the data reduction cookbook \citep{smoker_very_2012}. These artifacts in the K-band spectra were not observed in previous works in the H-band using this pipeline and as such may have a wavelength dependent affect, as the higher wavelength nIR is more susceptible to thermal instrument glow.

\subsubsection{Wavelength calibration}
\label{subsec:wave_cal}
There is a known issue with the wavelength calibration from the CRIRES Th-Ar calibrations \citep{kerber_laboratory_2009}, due to the low density of Th-AR lines in the near-infrared and the alignment with the detectors narrow wavelength range (e.g.\ CRIRES-POP \citep{nicholls_crirespop_2017}).
Therefore, we use the telluric absorption lines present in each observation as the wavelength reference. Instead of directly using the HITRAN database \citep{rothman_hitran2012_2013} for the line positions of the telluric spectra (e.g.~\citep{brogi_signature_2012,brogi_carbon_2014,dekok_detection_2013}), we use TAPAS atmospheric transmission models \citep{bertaux_tapas_2014} obtained for each observation. These in turn use the HITRAN database but include atmospheric profiles and physical measurements to model the telluric absorption strength.

@@

The wavelength solution was obtained by fitting a second order polynomial, shown to be sufficient for higher precision RV studies \citep[e.g.][]{bean_groundbased_2010, figueira_radial_2010}, to the centroid values \(\{\mu(x), \mu(\lambda)\} \) obtained from the telluric component of the observed spectra and telluric model respectively.

@@

We note that there are many variations on this wavelength-calibration technique including those integrated within programs such as TelFit \citet{gullikson_correcting_2014}, and ESOs Molecfit \citet{smette_molecfit_2015}, that perform telluric correction and re-calibrate the wavelength axis themselves.

@@

Secondly, we mask out any remaining artifacts present in the spectra and the centers of deep telluric lines where telluric correction was not corrected properly, sometimes resulting in "emission-like" peaks in the corrected spectrum. These factors combined result in masking out around a further 10\% of the observed spectra.

@@

We are aware that using these radii radii has its limitations, since as stated previously, there is a degeneracy in BD mass, age, and luminosity of the companion, and in particular a combination of radius-mass and radius-age relationships \citep{sorahana_radii_2013}. Using the PHOENIX-ACES model effective radius does not allow for any independent age constraints to be incorporated, or allow for any variability in the radii to account for uncertainties.
